Race Science in Mainstream Psychology, 1960-2010

### 2024-07-16 paper/paper.qmd
ready to submit
headers on table 1
commit before reformat

<!-- 
PNAS guidelines: <https://www.pnas.org/author-center/submitting-your-manuscript#article-types>

Research Report/Direct Submission: The preferred length of these articles is 6 pages, but PNAS allows articles up to a maximum of 12 pages. A standard 6-page article is approximately 4,000 words, 50 references, and 4 medium-size graphical elements (i.e., figures and tables).

- a manuscript file (in any format) including the following:
    title page (title, author list, classification, keywords)
    abstract
    significance statement
    main text
    references
    figures or tables with appropriate legends (may be uploaded separately)
    SI files (may be uploaded separately)
- contact and competing interest information for all authors
- data sharing plans (for all data, documentation, and code used in analysis)
- funding information and whether an open access license has been selected
- list of appropriate Editorial Board members, NAS members, and qualified reviewers (minimum of three each) who are experts in the paper's scientific area. (A brief justification for suggested reviewers is welcome, particularly for interdisciplinary papers)

- revised submission will require track changes version

figure sizes: 
Small: approximately 9 cm x 6 cm (3.5 in x 2.4 in)
Medium: approximately 11 cm x 11 cm (4.3 in x 4.3 in)
Large: approximately 18 cm x 22 cm (7.1 in x 8.7 in)

@@

*[TODO: 
- figure out renv::restore()
    - re-make
    - copy updated plots
]*

@@

| | | | |
|:--------|:----|:--------|-:|
| Thomas J. Bouchard, Jr. (1937-) | psychology | Univ. Minnesota | 184 |
| Brunetto Chiarelli (?-?) | anthropology | | 91 |
| Hans Eysenck (1916-1997) | psychology | King's College London | 661 |
| Robert A. Gordon (1932-) | sociology | Johns Hopkins | 0|
| Linda Gottfredson (1947-) | psychology | Univ. Delaware | 71 |
| Garrett Hardin (1915-2003) | ecology | UC Santa Barbara | 75 |
| Joseph M. Horn (1940-) | psychology | UT Austin | 68 |
| Lloyd Humphreys (1913-2003) | psychology | Univ. Illinois | 0 |
| Arthur Jensen (1923-2003) | psychology | UC Berkeley | 235 |
| Michael Levin (1943-) | philosophy | CCNY | 96 |
| Richard Lynn (1930-2023) | psychology | Ulster University\* | 288 |
| R. Travis Osborne (1913-2013) | psychology | Univ. Georgia | 59 |
| J. Phillippe Rushton (1943-2012) | psychology | Univ. Western Ontario | 277 |
| Audrey M. Shuey (1900-1977) | psychology | Randolph-Macon Women's College | 10 |
| Philip A. Vernon (1950-) | psychology | Univ. Western Ontario | 227 |
| Daniel Vining, Jr. (1944-) | demography | Univ. Pennsylvania | 33 |

@@

The public analysis repository, <https://github.com/dhicks/race-science> *DOI will go here]*, includes document metadata and documentwise counts of NLP-extracted noun phrases ("document-term matrices"), along with code to reproduce the analysis of the following sections.

>>>>

<!-- 
QSS submission guidelines: 
<https://direct.mit.edu/qss/pages/submission-guidelines>

- 300-word cover letter on significance and fit
- non-anonymous
- 200-word abstract
- 6 keywords
- number sections, subsections, and lines
- figures and tables near first ref
- author-date APA citations
- supplemental materials okay
- methods in "body," not end
- Acknowledgments, author contribution statements, competing interests statements, funding information, data availability statements, and appendices all at end

- Articles: original theoretical, empirical, or methodological research (typically between 5,000 and 8,000 words)

@@

@@

| name (birth-death) | field | affiliation | WoS doc. count |
|:--------|:----|:--------|-:|
| Thomas J. Bouchard, Jr. (1937-) | psychology | Univ. Minnesota | 184 |
| Brunetto Chiarelli (?-?) | anthropology | | 91 |
| Hans Eysenck (1916-1997) | psychology | King's College London | 661 |
| Robert A. Gordon (1932-) | sociology | Johns Hopkins | 0|
| Linda Gottfredson (1947-) | psychology | Univ. Delaware | 71 |
| Garrett Hardin (1915-2003) | ecology | UC Santa Barbara | 75 |
| Joseph M. Horn (1940-) | psychology | UT Austin | 68 |
| Lloyd Humphreys (1913-2003) | psychology | Univ. Illinois | 0 |
| Arthur Jensen (1923-2003) | psychology | UC Berkeley | 235 |
| Michael Levin (1943-) | philosophy | CCNY | 96 |
| Richard Lynn (1930-2023) | psychology | Ulster University\* | 288 |
| R. Travis Osborne (1913-2013) | psychology | Univ. Georgia | 59 |
| J. Phillippe Rushton (1943-2012) | psychology | Univ. Western Ontario | 277 |
| Audrey M. Shuey (1900-1977) | psychology | Randolph-Macon Women's College | 10 |
| Philip A. Vernon (1950-) | psychology | Univ. Western Ontario | 227 |
| Daniel Vining, Jr. (1944-) | demography | Univ. Pennsylvania | 33 |

@@

The public analysis repository, <https://github.com/dhicks/race-science> *[DOI will go here]*, includes document metadata and documentwise counts of NLP-extracted noun phrases ("document-term matrices"), along with code to reproduce the analysis of the following sections.
